### 2015-02-20 fundamentals/impl.tex
for example

In addition to the core functionality of the \Cyclus kernel, which is focused on
the set of capabilities needed to implement an agent-based simulation
with \gls{DRE}, a toolkit is provided that assists developers
and users with related simulation and nuclear engineering tasks. The toolkit is
an actively developed part of \Cyclus, with a primarily forward-looking
focus on supporting interesting \textit{in situ} metric analysis tools.

@@

A series of utility classes are provided to support demand-constrained agent
facility deployment. Symbolic function representations of linear,
exponential, and piecewise functions are supported via the
\Class{SymbFunctionFactory} class. Such functions are used with other toolkit
classes to determine commodity demand (e.g., power demand) from user input. Four
mix-in classes provide the basis for in-simulation deployment determination:
\Class{CommodityProducer}, \Class{CommodityProducerManager}, \Class{Builder},
\Class{BuildingManager}. The \Class{CommodityProducer} class provides an
interface for querying the \textit{prototypes} which have the
capacity to produce a given commdity. The \Class{CommodityProducerManager}
provides an interface for registering \Class{CommodityProducer}s and querying
the current capacity (supply) of a commodity. The \Class{Builder} class provides
an interface for querying which prototypes can be built and interacts with the
\Class{BuildingManager}, which orders prototypes to be built. The
\Class{BuildingManager} uses a simple minimum cost algorithm to determine how
many of each prototype, $y_i$, to build given a demand ($\Phi$), capacities
($\phi_i$), and costs ($c_i$).

>>>>

In addition to the core functionality of the \Cyclus kernel, which is focused on
the set of capabilities needed to implement an agent-based simulation
with \gls{DRE}, a toolkit is provided to assist developers
and users with related simulation and nuclear engineering tasks. The toolkit is
an actively developed part of \Cyclus, with a primarily forward-looking
focus on supporting interesting \textit{in situ} metric analysis tools.

@@

A series of utility classes are provided to support demand-constrained agent
facility deployment. For example, symbolic function representations of linear,
exponential, and piecewise functions are supported via the
\Class{SymbFunctionFactory} class. Such functions are used with other toolkit
classes to determine commodity demand (e.g., power demand) from user input. Four
mix-in classes provide the basis for in-simulation deployment determination:
\Class{CommodityProducer}, \Class{CommodityProducerManager}, \Class{Builder},
\Class{BuildingManager}. The \Class{CommodityProducer} class provides an
interface for querying the \textit{prototypes} which have the
capacity to produce a given commdity. The \Class{CommodityProducerManager}
provides an interface for registering \Class{CommodityProducer}s and querying
the current capacity (supply) of a commodity. The \Class{Builder} class provides
an interface for querying which prototypes can be built and interacts with the
\Class{BuildingManager}, which orders prototypes to be built. The
\Class{BuildingManager} uses a simple minimum cost algorithm to determine how
many of each prototype, $y_i$, to build given a demand ($\Phi$), capacities
($\phi_i$), and costs ($c_i$).
